--- 
title: "Reading Notes"
author: "Hui Lin"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib]
biblio-style: apalike
link-citations: yes
description: "This is my reading notes since 2009"
---

# Reading List

It is my reading list since 2009. The reading notes are arranged according to book category.There are tons of paper notes need to be electrolyzed and I will keep working on it in my spare time. I know nothing about library science but the goal here is to make things more structured and easy to search which will be especially helpful when I am traveling. Good luck!  

My personal comments will start with "Hui:". Sometimes I summarize the contents with my own words. It is great if you find any of those notes useful for you as well. I thank all my friends who recommended great books to me. If you have any questions or awesome books that you keenly want to share, feel free to email me at: longqiman@gmail.com. Thank you in advance!

```{r,echo=FALSE}
library(DT)
dat<-read.csv("/Users/happyrabbit/Dropbox/book/ReadingListHui.csv")
# Code used to assign ID
#dat<-dat[order(dat$CATE_CODE,decreasing=F),]
#library(nnet)
#res<-class.ind(dat$CATE_CODE)
#for (i in 1:ncol(res)){
#res[,i]<-res[,i]*cumsum(res[,i])/100
#}
#dat$ID<-paste(dat$CATE_CODE,apply(res,1,sum),sep="")
#str(dat)
#setwd("/Users/happyrabbit/Dropbox/book/")
#write.csv(dat,"ReadingListHui.csv",row.names=F)
```

```{r,echo=FALSE}
datatable(subset(dat,select=c("Name","ID","Category","Author","Progress","Priority")))
```


- **Name**: Book name
- **ID**: Book index number 
- **Category**: Book category  
- **Author**: Author of the book
- **Progress**: My reading progress(from 0% [haven't started] to 100% [finished])
- **Priority**: My reading priority

## Rules of Generating book ID

1. **Category code** + **Number**
1. **Number** was origionally assigned as the rank of the book in its category devided by 100 (i.e rank/100)
1. For new book
      1. search for the maximum number in that category (`mn`)
      1. use `mn+0.01` as number for the new book
      
## Basic Statistical Analysis

Here is a plot for counts of books in each category......Obviously, my favorite is "Philosophy and Psychology" .  I have few books on "Politics","Law", "Gender", "Data Science" and "Medicine"......Statistics (31), Data Science (5) and IT(7) [**SDT** area], all these three added together is about the size of "Business & Economics". I am a little surprised. Some possible insights are (not all of them necessary to be true):
 
1. Professional area/degree don't tell how a person spend time
1. Scientists read more journal papers and technique reports in corresponding area than books
1. There are not as many books in **SDT** as in some other areas   
1. I didn’t spend enough time in **SDT** 
1. I need to work harder on **SDT** 

```{r, echo=FALSE,message=FALSE,warning=FALSE}
dat$Category[dat$Category=="Novels and Plays-detective"]<-"Novels and Plays"
dat$Category[dat$Category=="Novel"]<-"Novels and Plays"
booktb<-data.frame(table(as.character(dat$Category)))
names(booktb)<-c("Category","Counts")
booktb<-booktb[order(booktb$Counts,decreasing = T),]
library(ggplot2)
ggplot(booktb, aes(x=reorder(Category,Counts), y=Counts, fill=Category)) + 
  geom_bar(stat="identity")+ coord_flip()+ ylab("Counts") + xlab("Category")+ theme(legend.position="none")
```

Here is a plot showing the percentage of books I have started (or finished) across different categories.

```{r, echo=FALSE,message=FALSE,warning=FALSE}
Progress<-rep("Started",nrow(dat))
idx<-which(dat$Progress=="")
Progress[idx]<-"Not-Started"
dat$Status<-Progress
ggplot(dat, aes(Category,fill=Status)) +
geom_bar(position="fill")+ coord_flip()+ ylab("Percentage") + xlab("Category")

```

```{r, echo=FALSE}
#bookp<-data.frame(table(dat$Category,dat$Progress))
#head(bookp)
#booktb<-booktb[order(booktb$Counts,decreasing = T),]
#booktb
```
